---
title: "Comparison of two PHI datasets (changes in the dataset over time)"
author: "Petra Hermankova"
date: "27/08/2020"
output: rmarkdown::github_document
---

*Setting up the environment*
```{r setup, echo=TRUE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE)
devtools::install_github("sdam-au/sdam")

library(tidyverse)
library(sdam)
library(jsonlite)
library(getPass)
```

# Loading up the datasets
1. Input your sciencedata.dk username - type directly into the RStudio console
```{r, echo = FALSE }
user <- readline("your sciencedata username: ")
```

## Dataset 1
2. Make the request (you will be asked for password in a new pop-up window)
```{r, echo = FALSE }
resp = request("PHI_enriched_2020-08-27.json", path="/sharingin/648597@au.dk/SDAM_root/SDAM_data/PHI/", method="GET", cred=c(user, getPass("your sciencedata password: ")))
```

```{r}
list_json <- jsonlite::fromJSON(resp)
PHI_aug = as.data.frame(list_json)
PHI_aug
```
## Dataset 2
```{r, echo = FALSE }
resp2 = request("PHI_enriched_2020-06-29.json", path="/sharingin/648597@au.dk/SDAM_root/SDAM_data/PHI/", method="GET", cred=c(user, getPass("your sciencedata password: ")))
```

```{r}
list_json2 <- jsonlite::fromJSON(resp2)
PHI_jun = as.data.frame(list_json2)
PHI_jun
```

# Compare the two datasets 

## How many more new inscriptions were added in July?
```{r}
nrow(PHI_aug) - nrow(PHI_jun)
```

## What column names are different?
```{r}
setdiff(names(PHI_jun), names(PHI_aug))
```

## What column names are identical?
```{r}
intersect(names(PHI_jun), names(PHI_aug))
```

### Select only the columns from the wider dataset that are in both (so they have idential structure to do the comparison:
```{r}
PHI_june<- PHI_jun[intersect(names(PHI_jun), names(PHI_aug))]
```

## Checking the datatypes
```{r}
is(PHI_june)
is(PHI_aug)
```

## Subsetting for testing
```{r}
small_aug<- head(PHI_aug)
small_june<- head(PHI_june)
```
### Saving the subsets to Sciencedata for debugging

```{r}
small_aug_json <- jsonlite::toJSON(small_aug) 
write(small_aug_json, file="PHI_small_aug.json")
user <- readline("your sciencedata username: ")
request("PHI_small_aug.json", path="/sharingout/648597@au.dk/SDAM_root/SDAM_data/PHI/",
        method="PUT", cred=c(user, getPass("your sciencedata password: ")))
```

```{r}
small_june_json <- jsonlite::toJSON(small_june) 
write(small_june_json, file="PHI_small_june.json")
user <- readline("your sciencedata username: ")
request("PHI_small_june.json", path="/sharingout/648597@au.dk/SDAM_root/SDAM_data/PHI/",
        method="PUT", cred=c(user, getPass("your sciencedata password: ")))
```

## Unlisting > flattening the list into a dataframe

1. tidyr::unnest
```{r}
# https://stackoverflow.com/a/56989523

unnested_small_aug<- small_aug %>% unnest_auto(note) %>% unnest(cols = c(URL, Book, Text, hdr2, tildeinfo, note, lines, metadata, data, filename, PHI_ID))
unnested_small_aug
```

```{r}
# https://stackoverflow.com/a/62683600/14219893 for multiple columns with nested lists

unnested_small_june <- small_june %>% 
  unnest_longer(hdr2) %>% 
  unnest_longer(note) %>% 
  unnest_longer(URL) %>% 
  unnest_longer(Book) %>% 
  unnest_longer(Text) %>% 
  unnest_longer(tildeinfo) %>% 
  unnest_longer(lines) %>% 
  unnest_longer(metadata) %>% 
  unnest_longer(data) %>% 
  unnest_longer(filename) %>% 
  unnest_longer(PHI_ID) 
```



## Comparing the two datasets using compareDF 
https://CRAN.R-project.org/package=compareDF
https://github.com/alexsanjoseph/compareDF

```{r}
#install.packages("compareDF")
#devtools::install_github('alexsanjoseph/compareDF')
library(compareDF)
library(htmlTable)
```
# Making sure all datasets have identical columns, exclusing the redundants ones

```{r}
intersect(names(unnested_small_aug), names(unnested_small_june))
unnested_small_june2<- unnested_small_june[intersect(names(unnested_small_june), names(unnested_small_aug))]
```

# Do a git style comparison between two data frames of similar columnar structure (new dataset first, old second)
```{r}
small_compared <- compare_df(unnested_small_aug, unnested_small_june2)
```

## Show comparison in a table, where red means "missing in the new dataset" and green "new addition to the new dataset" 
```{r}
create_output_table(small_compared)
small_compared
```
## Repeat the same for the large dataset - DOES NOT WORK

# https://stackoverflow.com/a/62683600/14219893 for multiple columns with nested lists

```{r}

unnested_PHI_aug <- PHI_aug %>% 
  unnest_longer(hdr2) %>% 
  unnest_longer(note) %>% 
  unnest_longer(URL) %>% 
  unnest_longer(Book) %>% 
  unnest_longer(Text) %>% 
  unnest_longer(tildeinfo) %>% 
  unnest_longer(lines) %>% 
  unnest_longer(metadata) %>% 
  unnest_longer(data) %>% 
  unnest_longer(filename) %>% 
  unnest_longer(PHI_ID)
```

```{r}
PHI_june_json <- jsonlite::toJSON(PHI_june) 
write(PHI_june_json, file="PHI_june_2020.json")

PHI_aug_json <- jsonlite::toJSON(PHI_aug) 
write(PHI_aug_json, file="PHI_aug_2020.json")
```

